### 2025-03-01 LaTeX/template.tex
Added LaTeX template to paper

% -*- Mode:TeX -*-
% LaTeX template for CinC papers                   v 1.1a 22 August 2010
%
% To use this template successfully, you must have downloaded and unpacked:
%       http://www.cinc.org/authors_kit/papers/latex.tar.gz
% or the same package in zip format:
%       http://www.cinc.org/authors_kit/papers/latex.zip
% See the README included in this package for instructions.
%
% If you have questions, comments or suggestions about this file, please
% send me a note!  George Moody (george@mit.edu)
%
\documentclass[twocolumn]{cinc}
\usepackage{graphicx}
\begin{document}
\bibliographystyle{cinc}

% Keep the title short enough to fit on a single line if possible.
% Don't end it with a full stop (period).  Don't use ALL CAPS.
\title{The Title Should Be in This Format and Should Be \\
Clear Without Abbreviations or Period at End}

% Both authors and affiliations go in the \author{ ... } block.
% List initials and surnames of authors, no full stops (periods),
%  titles, or degrees.
% Don't use ALL CAPS, and don't use ``and'' before the name of the
%  last author.
% Leave an empty line between authors and affiliations.
% List affiliations, city, [state or province,] country only
%  (no street addresses or postcodes).
% If there are multiple affiliations, use superscript numerals to associate
%  each author with his or her affiliations, as in the example below.

\author {Jacob Collins$^{1}$, Jaime Raigoza$^{1}$, Sam Siewert$^{1}$ \\
\ \\ % leave an empty line between authors and affiliation
 $^1$ California State University, Chico, United States of America (note - full address at end of paper)}

\maketitle

% LaTeX inserts the ``Abstract'' heading in the proper style and
% sets the text of the abstract in italics as required.
\begin{abstract}

    Center the word Abstract and print it in Times New Roman 11-point size
    and in bold.

% Of course, you must insert blank lines
% between the paragraphs of your LaTeX input file, since this is the
% only way to indicate paragraph boundaries.  Make sure that no blank
% lines appear between paragraphs in the formatted output, however.)
% 
% 
    The abstract and all other text (except as indicated in
    Table~\ref{tab:font}) are printed in a 10-point size. The text of the
    abstract (and only the abstract) should be in italics. Begin all
    paragraphs with a 1 pica (4 mm, 1/6 inch) indentation.

    Do not add blank line spaces between paragraphs in the abstract or
    anywhere else in your article.

    The abstract with its heading should not be more than 100 mm long,
    which is equivalent to 25 lines of text. Leave 2 line spaces at the
    bottom of the abstract before continuing with the next heading.

\end{abstract}
% LaTeX inserts the extra space here automatically.

\section{Introduction}
% Section numbering is automatic.  The examples on the next page
% illustrate how to make subsections.

Leave one line space above and below all headings from now on.

Number your sections (e.g., 1.  1.1.  1.2.  - note the decimal points) as
illustrated. Start the text of section headings after a 12 mm (0.5 inch)
tab.

% LaTeX converts the reference tag ('WP-89') into a reference number,
% which it inserts in the formatted text as '[1]'.  If you use BibTeX
% to handle references, BibTeX finds a reference with the tag 'WP-89'
% in 'refs.bib', and inserts that reference into the ``References''
% section in CinC style.
%

\subsection{Print font}

Please use Times New Roman font. Use of this font by all authors ensures
that our papers are produced consistently with a professional appearance.

 \subsection{ Print size}

Follow the information given in Table 1 for all font print sizes and styles.

\section{Title block}

On the first page, the title, authors, and institution(s) should be
positioned and aligned as above.

\subsection{Title}

Do not use abbreviations in the title and keep to one or two
lines. Remember that the title should be easily understood when cited as a
reference in another publication. Make sure the title is centered. Note the
use of capital letters, as shown in the example above. Do not place a
period at the end of the title.

\subsection{ Author line}

If it is essential to link authors to different institutions, use a small
superscript at the end of each family name and link to each institution. No author degrees should be
included. No periods should appear in the author line.

 \subsection{ Institution address}

 This address identifies the institution(s). It is not a postal address and
 should not contain postal or zip codes. A full postal address is given at
 the end of the paper under `Address for correspondence'. Do not put line
 spaces between address lines or use a period at the end.

 \section{ Tables and figures}
\subsection{Tables} 
\vspace{-4 mm}
\begin{table}[htbp]
\caption{\label{tab:font} Print sizes for different parts of the paper.}
\vspace{4 mm}
\centerline{\begin{tabular}{lcr} \hline\hline
Text    & Point size    & Type \\ \hline
Title   & 14 point      & Bold \\
Author line     & 12 point      & \\
Institution line        & 12 point      & \\
Abstract heading        & 11 point      & Bold \\
All other headings      & 12 point      & Bold \\
Abstract text   & 10 point      & Italic \\
References and address  & 9 point       & \\
All other text  & 10 point      & \\ \hline\hline
\end{tabular}}

\end{table}

Keep \ the layout of \ tables simple. Avoid  heavy lines and boxes.

\subsection{ Figures}

Figures can fit across both columns if necessary. Include all figures, with
captions, in the text document at their desired locations, i.e., not at the
end. To make sure that all labels are legible, use at least 9-point
font. Use a line thickness of at least 0.5 mm in the body of the figure.

\begin{figure}[h]
%\centering
\includegraphics[width=7.9cm]{graph.png}
\caption{Put the figure legend here, at the bottom, clearly describing the
  figure.}
\label{FIGURA1}
\end{figure}

Leave a line space after a figure legend. Be cautious with background
colors in figures because they can make printed figures hard to read.

\section{Final page}

The text on the final page should be arranged so that both columns are
approximately the same length.

\balance

\section{Style of references}

All references should be included in the text in square brackets in their
order of appearance, e.g., \cite{tag}, \cite{tag,ito}, or
\cite{tag,ito,fardel,buncombe}. In the reference list, use the Vancouver
style (see IEEE Transactions on Biomedical Engineering or Annals of
Biomedical Engineering). The main goal is to be consistent in your
formatting of references.

References to \emph{Computers in Cardiology} (or \emph{Computing in
  Cardiology}) proceedings should include the volume and page numbers,
unless no page numbers were included (post-2016). Check the style in the
examples below.

\section{ Final checks }

Print this template without resizing or centering and compare with your
final paper to ensure that you have not accidentally changed margins and
layout.

\section*{Acknowledgments}  
% This section is not numbered.
% 
Give any acknowledgments here.

% LateX generates the ``References'' heading automatically and switches
% to 9 point type for the bibliography.  Please  use BibTeX and
% follow the examples in the sample 'refs.bib' file to enter your references.
\bibliography{refs}

% If you don't use BibTeX (why not?) , comment out or remove the previous
% line, and uncomment the following lines up to the ``}\end{bibliography}''
% line below:
%\begin{thebibliography}{99}{ %\small
% \bibitem{tag} (General form) J. K. Author, ``Name of paper,''
%   \emph{Abbrev. Title of
%   Periodical}, vol. x, no. x, pp. xxx--xxx, Abbrev. Month, year.

% \bibitem{ito}  M. Ito et al., ``Application of amorphous oxide TFT to
%   electrophoretic display,'' \emph{J. Non-Cryst. Solids}, vol. 354, no. 19,
%   pp. 2777--2782, Feb. 2008.

% \bibitem{fardel}  R. Fardel, M. Nagel, F. Nuesch, T. Lippert, and
%   A. Wokaun, ``Fabrication of organic light emitting diode pixels by
%   laser-assisted forward transfer,'' \emph{Appl. Phys. Lett.}, vol. 91,
%   no. 6, Aug. 2007, Art. no. 061103.

% \bibitem{buncombe} J. U. Buncombe, ``Infrared navigation Part I: Theory,''
%     \emph{IEEE Trans. Aerosp. Electron. Syst.}, vol. AES-4, no. 3,
%     pp. 352--377, Sep. 1944.

% Uncomment the following line if you are not using BibTeX.
%}\end{thebibliography}

% LaTeX inserts the ``Address for correspondence'' heading.
\begin{correspondence}
My Name\\
My Full postal address\\
My E-mail address
\end{correspondence}

\end{document}

### 2025-03-02 LaTeX/paper.tex
Finished outline for paper

--- 2025-03-01 LaTeX/template.tex
@@
 % Don't end it with a full stop (period).  Don't use ALL CAPS.
-\title{The Title Should Be in This Format and Should Be \\
-Clear Without Abbreviations or Period at End}
+\title{Leveraging Grover's Algorithm for Efficient Prime Decomposition}
 
@@
 
+% \author {Jacob Collins$^{1}$, Jaime Raigoza$^{1}$, Sam Siewert$^{1}$ \\
 \author {Jacob Collins$^{1}$, Jaime Raigoza$^{1}$, Sam Siewert$^{1}$ \\
 \ \\ % leave an empty line between authors and affiliation
- $^1$ California State University, Chico, United States of America (note - full address at end of paper)}
+ $^1$ California State University, Chico, United States of America (note- full address at end of paper)}
 
@@
 
-    Center the word Abstract and print it in Times New Roman 11-point size
-    and in bold.
+  In quantum computing, SP (semiprime) factoring is typically performed 
+  with Shor's algorithm, but it is possible to achieve the same results
+  more efficientily via Grover's algorithm\cite{whitlock2023quantumfactoringalgorithmusing}.
 
-% Of course, you must insert blank lines
-% between the paragraphs of your LaTeX input file, since this is the
-% only way to indicate paragraph boundaries.  Make sure that no blank
-% lines appear between paragraphs in the formatted output, however.)
-% 
-% 
-    The abstract and all other text (except as indicated in
-    Table~\ref{tab:font}) are printed in a 10-point size. The text of the
-    abstract (and only the abstract) should be in italics. Begin all
-    paragraphs with a 1 pica (4 mm, 1/6 inch) indentation.
-
-    Do not add blank line spaces between paragraphs in the abstract or
-    anywhere else in your article.
+  Grover's Algorithm is used to search for one (or many) given state(s)
+  among some set of possible outputs. In this case, given some semiprime,
+  Grover's algorithm may be used to find the prime factors.
 
@@
 \section{Introduction}
-% Section numbering is automatic.  The examples on the next page
-% illustrate how to make subsections.
 
-Leave one line space above and below all headings from now on.
+What are we doing, broadly?
 
-Number your sections (e.g., 1.  1.1.  1.2.  - note the decimal points) as
-illustrated. Start the text of section headings after a 12 mm (0.5 inch)
-tab.
+Include a figure of our circuit diagram and briefly describe what it 
+does, and how it does it.
 
-% LaTeX converts the reference tag ('WP-89') into a reference number,
-% which it inserts in the formatted text as '[1]'.  If you use BibTeX
-% to handle references, BibTeX finds a reference with the tag 'WP-89'
-% in 'refs.bib', and inserts that reference into the ``References''
-% section in CinC style.
-%
+  \subsection{Motivation}
 
-\subsection{Print font}
+  Why are we replicating the research, why is this important.
 
-Please use Times New Roman font. Use of this font by all authors ensures
-that our papers are produced consistently with a professional appearance.
+  \subsection{Semiprime Factoring}
 
- \subsection{ Print size}
+  What is SP factoring and why is it important. RSA, etc.
 
-Follow the information given in Table 1 for all font print sizes and styles.
+\section{Methodology}
 
-\section{Title block}
+Quantum algorithms take advantage of superposition and entanglement,
+allowing this form of computation to perform operations on many 
+values simultaneously, rather than checking each value individually
+as is necessary in classical algorithms.
 
-On the first page, the title, authors, and institution(s) should be
-positioned and aligned as above.
+  \subsection{Using Grover's Algorithm to Invert Functions}
 
-\subsection{Title}
+  Describe how Grover's works and show figures of a generalized
+  circuit for Grover's to invert functions
 
-Do not use abbreviations in the title and keep to one or two
-lines. Remember that the title should be easily understood when cited as a
-reference in another publication. Make sure the title is centered. Note the
-use of capital letters, as shown in the example above. Do not place a
-period at the end of the title.
+  \subsection{Semiclassical Arithmetic}
 
-\subsection{ Author line}
+  Describe our original approach- bitwise addition, registers, operations, etc.
 
-If it is essential to link authors to different institutions, use a small
-superscript at the end of each family name and link to each institution. No author degrees should be
-included. No periods should appear in the author line.
+  Mention why an alternative approach was needed.
 
- \subsection{ Institution address}
+  \subsection{Arithmetic in the Quantum Fourier Domain}
 
- This address identifies the institution(s). It is not a postal address and
- should not contain postal or zip codes. A full postal address is given at
- the end of the paper under `Address for correspondence'. Do not put line
- spaces between address lines or use a period at the end.
+  Describe the updated methods of quantum arithmetic, and how it solved the 
+  previous problems.
 
- \section{ Tables and figures}
-\subsection{Tables} 
-\vspace{-4 mm}
-\begin{table}[htbp]
-\caption{\label{tab:font} Print sizes for different parts of the paper.}
-\vspace{4 mm}
-\centerline{\begin{tabular}{lcr} \hline\hline
-Text    & Point size    & Type \\ \hline
-Title   & 14 point      & Bold \\
-Author line     & 12 point      & \\
-Institution line        & 12 point      & \\
-Abstract heading        & 11 point      & Bold \\
-All other headings      & 12 point      & Bold \\
-Abstract text   & 10 point      & Italic \\
-References and address  & 9 point       & \\
-All other text  & 10 point      & \\ \hline\hline
-\end{tabular}}
+  Figures to visualize how the weighted phase shifts work to produce
+  expected results matching addition, scaled addition, and register 
+  multiplication.
 
-\end{table}
+\section{Results and Discussion}
 
-Keep \ the layout of \ tables simple. Avoid  heavy lines and boxes.
+Include some charts showing our runtime and qubit requirements vs N.
 
-\subsection{ Figures}
+  \subsection{Accuracy and Limitations}
 
-Figures can fit across both columns if necessary. Include all figures, with
-captions, in the text document at their desired locations, i.e., not at the
-end. To make sure that all labels are legible, use at least 9-point
-font. Use a line thickness of at least 0.5 mm in the body of the figure.
+  How precise and accurate were our measurements. Mention edge-cases like
+  square semiprimes, etc.
 
-\begin{figure}[h]
-%\centering
-\includegraphics[width=7.9cm]{graph.png}
-\caption{Put the figure legend here, at the bottom, clearly describing the
-  figure.}
-\label{FIGURA1}
-\end{figure}
+  How many qubits were we able to simulate, i.e., how large of semiprimes
+  can we factor with our current systems.
 
-Leave a line space after a figure legend. Be cautious with background
-colors in figures because they can make printed figures hard to read.
+  \subsection{Comparison to Shor's Algorithm}
 
-\section{Final page}
+  List strengths and weaknesses of Shor's, i.e., more documentation, more
+  examples, larger code base to reference, but ours is faster and uses less
+  qubits.
+
+\section{Conclusion}
+
+\section{Future Work}
 
@@
 
-\section{Style of references}
-
-All references should be included in the text in square brackets in their
-order of appearance, e.g., \cite{tag}, \cite{tag,ito}, or
-\cite{tag,ito,fardel,buncombe}. In the reference list, use the Vancouver
-style (see IEEE Transactions on Biomedical Engineering or Annals of
-Biomedical Engineering). The main goal is to be consistent in your
-formatting of references.
-
-References to \emph{Computers in Cardiology} (or \emph{Computing in
-  Cardiology}) proceedings should include the volume and page numbers,
-unless no page numbers were included (post-2016). Check the style in the
-examples below.
-
-\section{ Final checks }
-
-Print this template without resizing or centering and compare with your
-final paper to ensure that you have not accidentally changed margins and
-layout.
-
 \section*{Acknowledgments}  
@@
 % 
-Give any acknowledgments here.
+Acknowledge the source paper.
 
@@
 \begin{correspondence}
-My Name\\
-My Full postal address\\
-My E-mail address
+Jacob Collins\\
+1565 Filbert Ave\\
+jbcollins@csuchico.edu
 \end{correspondence}

### 2025-03-02 LaTeX/paper.tex
Updated paper outline

@@
 
+\section{Goals}
+
+Demonstration of quantum advantage, or at least determination of
+the problem scale at which quantum advantage will pull ahead.
+
+\section{Literature Review}
+
+Discuss existing methods of SP factoring- both quantum and classical.
+
+Mention reference paper, QFT arithmetic, CUDA-Q docs, shor's, grover's.
+
 \section{Methodology}
@@
 
+What have we learned so far, what does it mean, at what problem scale might
+we see quantum advantage based on our results, etc.
+
 \section{Future Work}
 
-The text on the final page should be arranged so that both columns are
-approximately the same length.
+Implementation of the optimization with M, S, p, and q, rather than just 
+a and b from N.
 

### 2025-03-02 LaTeX/paper.tex
Updated grover's definitions and some methodology

@@
 % Don't end it with a full stop (period).  Don't use ALL CAPS.
-\title{Leveraging Grover's Algorithm for Efficient Prime Decomposition}
+\title{Quantum Semiprime Factorization: Leveraging Grover's Algorithm for Efficient Prime Decomposition}
 
@@
   with Shor's algorithm, but it is possible to achieve the same results
-  more efficientily via Grover's algorithm\cite{whitlock2023quantumfactoringalgorithmusing}.
+  more efficientily via Grover's algorithm\cite{quantum_factoring, grover}.
 
-  Grover's Algorithm is used to search for one (or many) given state(s)
-  among some set of possible outputs. In this case, given some semiprime,
-  Grover's algorithm may be used to find the prime factors.
+  Key terms: Semiprime, superposition, entanglement, RSA encryption, (add more).
 
@@
 
-What are we doing, broadly?
+The practicality of applied quantum computing is a topic of much debate,
+and there are not many examples of quantum computers being able to out-perform
+their classical counterpart, yet.
+
+Quantum algorithms have been in development at a theoretical level for
+decades, but the application of these methods is still in early stages.
+It is quite common to find code which implements a quantum algorithm like
+Grover's or Shor's, but very often these programs are hard-coded, and only
+work for a small handful of specific values\cite{shors_ibm}.
 
@@
 
+  Quantum computers are a technology very much still under development. 
+  As such, one of the major limitations for applied quantum computing is 
+  the number of qubits required to perform a given task. If it can be verified 
+  that SP factoring with Grover's algorithm uses significantly less qubits than
+  Shor's, then the application of these techniques will be feasible far sooner.
+
   \subsection{Semiprime Factoring}
@@
 
-Demonstration of quantum advantage, or at least determination of
-the problem scale at which quantum advantage will pull ahead.
+The goal of this research endeavor is to estimate the problem scaling point
+at which some quantum algorithm may be able to out-perform our best classical
+solution to the same problem.
+
+Grover's algorithm has an incredibly wide range of potential use-cases,
+and an intention for this paper is to provide a generalized reference point
+for how Grover's algorithm may be used to invert any function.
 
@@
 
-Discuss existing methods of SP factoring- both quantum and classical.
+  \subsection{Grover's Algorithm}
 
-Mention reference paper, QFT arithmetic, CUDA-Q docs, shor's, grover's.
+  Grover's Algorithm is a quantum computing method 
+  that can be used to search a database in $O(\sqrt{n})$ time 
+  rather than the naive classical time complexity of $O(n)$\cite{grover}.
 
-\section{Methodology}
+  Given a function $f(x)=y$, where $x$ is unknown (index, prime factors, 
+  sum components, etc.), and $y$ is known (array value, semiprime/product, 
+  sum, etc.), Grover's algorithm effectively takes the role of $f'(y)$, 
+  allowing for a potential speedup in finding whatever input(s) to $f(x)$
+  will return $y$.
+
+  This speedup comes from the fact that Grover's algorithm requires 
+  $O(\sqrt{y})$ iterations, each of which have a time complexity proportional
+  to that of $f(x)$.
+
+  \subsection{Shor's Algorithm}
+
+  Description of Shor's algorithm.
+
+  \subsection{Quantum Factoring Algorithm with Grover Search}
+
+  S. Whitlock, et al. present a method of SP factoring with Grover's
+  algorithm. The implementation in their paper is highly optimized,
+  and modifies the target value in their circuit from some semiprime $N$,
+  to $M$, a reduced number uniquely tied to $N$, which has prime factors
+  $p$ and $q$.
+
+  While this approach is admirable, it introduces a level of complexity 
+  that may hinder a learner's understanding of the mechanics at play,
+  so the implementation shown in section \ref{sec:Methodology} forgoes
+  this abstraction from $N$ to $M$, and instead implements an oracle which
+  searches directly for prime factors $a$ and $b$ of a semiprime $N$.
+
+\section{Methodology} \label{sec:Methodology}
 
 Quantum algorithms take advantage of superposition and entanglement,
-allowing this form of computation to perform operations on many 
-values simultaneously, rather than checking each value individually
-as is necessary in classical algorithms.
+which enables many methods of computation which are otherwise impossible
+with a classical computer. For example, by placing a set of $n$ qubits 
+(otherwise known as a qubit \textbf{register}) in superposition, that register
+simultaneously represents every value which can be represented in $n$ bits,
+until measured. Once measured, a register in uniform superposition will 
+collapse into one of these states with equal likelihood.
 
-  \subsection{Using Grover's Algorithm to Invert Functions}
+In a given register $R_n$ with $n$ qubits, values are represented in binary,
+such, for example, if some number $N=3$ were to be represented classically
+with $n=4$ bits, it might be seen in binary as $0011$, and on a qubit
+register that number may be represented similarly as $| 0011 \rangle$.
+
+  \subsection{Grover's Algorithm for General Function Inversion}
+
+  Mention unitary matrices.
 
@@
   circuit for Grover's to invert functions
+
+  Reference figure 1.
+
+  Operations can be performed on a register in superposition, and these operations
+  will affect each potential state individually. This property is utilized by
+  Grover's Oracle to selectively target specific states which match the target
+  value, and the diffuser is used to increase the probability of measuring the
+  inputs which resulted in this marked target state.
+
+  \begin{figure}[h]
+  %\centering
+  \includegraphics[width=7.9cm]{grover_inversion.png}
+  \caption{General circuit diagram for Grover's Algorithm, used to find 
+  the inputs $x, y$ for which $f(x,y)=z$, for some known $z$.}
+  \label{FIGURA1}
+  \end{figure}
+
+  Include one figure showing the oracle, and one figure showing the diffuser.
 
@@
   Mention why an alternative approach was needed.
+
+  Include a drawing of the circuit.
 

### 2025-03-02 generate_drawings/generate_drawings.cpp
Added figures for diffuser and oracle

@@ -1,0 +1,404 @@
+/**********************************
+ * Description: 
+ *      Using grover's algorithm to invert QFT multiplication
+ *      to achieve quantum SP factoring.
+ * Note:
+ *      Must be updated with methods from [this paper](https://arxiv.org/pdf/2312.10054)
+ *      to reduce error and increase qubit efficiency.
+ *      ^ IP in `factor.cpp`
+ * Author: Jacob Collins
+ **********************************/
+
+#include <cudaq.h>
+#include <cudaq/algorithms/draw.h>
+
+#include <math.h>
+#include <numbers>
+#include <algorithm>
+#include <chrono>
+#include <cmath>
+#include <iostream>
+#include <sstream>
+#include <string>
+#include <vector>
+
+#define ENABLE_DEBUG true // Displays full bitwise output
+#define ENABLE_CIRCUIT_FIG true
+#define ENABLE_MISC_DEBUG false
+#define ENABLE_STATEVECTOR false
+
+//#define NUMBER_OF_SHOTS 100
+#define NUMBER_OF_SHOTS 1
+#define NUM_RESULTS_DISPLAYED 5
+
+/**************************************************
+******************* HELPER FUNCS ******************
+***************************************************/
+
+// Convert some value to a string
+template <typename T>
+std::string to_string(T value) {
+  std::stringstream ss;
+  ss << value;
+  return ss.str();
+}
+
+// Convert nanoseconds to a string displaying subdivisions of time
+std::string format_time(long long nanoseconds, bool sep=false) {
+  long long milliseconds = nanoseconds / 1'000'000;  // From ns to ms
+  long long seconds = milliseconds / 1'000;          // From ms to seconds
+  milliseconds = milliseconds % 1'000;               // Remaining milliseconds
+
+  long long remaining_nanoseconds =
+      nanoseconds % 1'000'000;  // Remaining nanoseconds
+  long long microseconds = remaining_nanoseconds / 1'000;  // From ns to µs
+  remaining_nanoseconds = remaining_nanoseconds % 1'000;   // Remaining ns
+
+  // Create the formatted string
+  if (sep) {
[…]

### 2025-03-02 LaTeX/paper.tex
Talked about shor's and added figures to paper

@@
 % \author {Jacob Collins$^{1}$, Jaime Raigoza$^{1}$, Sam Siewert$^{1}$ \\
-\author {Jacob Collins$^{1}$, Jaime Raigoza$^{1}$, Sam Siewert$^{1}$ \\
+\author{Jacob Collins$^{1}$, Jaime Raigoza$^{1}$, Sam Siewert$^{1}$ \\
 \ \\ % leave an empty line between authors and affiliation
- $^1$ California State University, Chico, United States of America (note- full address at end of paper)}
+ $^1$ California State University, Chico, United States (note- full address at end of paper)}
 
@@
 Grover's algorithm has an incredibly wide range of potential use-cases,
-and an intention for this paper is to provide a generalized reference point
-for how Grover's algorithm may be used to invert any function.
+and an intention for this paper is to provide a generalized reference
+for how Grover's algorithm may be used to invert a given function.
 
@@
   sum components, etc.), and $y$ is known (array value, semiprime/product, 
-  sum, etc.), Grover's algorithm effectively takes the role of $f'(y)$, 
-  allowing for a potential speedup in finding whatever input(s) to $f(x)$
-  will return $y$.
+  sum, etc.), Grover's algorithm effectively takes the role of $f'(y)=x$, 
+  allowing for a potential speedup in finding whatever input (s) to $f(x)$
+  will return $y$, provided that it is much faster to compute $f(x)$ than
+  whatever classical methods might be used to otherwise solve for $x$ given $y$.
 
@@
 
-  Description of Shor's algorithm.
+  Shor's algorithm is the most well-known approach to prime factorization
+  in quantum computing. However, there are many drawbacks to this approach,
+  the most notable of which being the need to take measurements mid-circuit
+  and essentially re-run with new values afterwards, which introduces a 
+  significant amount of overhead. Even recently improved versions of Shor's
+  algorithm still require a minimum of $2n+1$ qubits, and tend to be 
+  extremely sensitive to noise, which leads to high error\cite{quantum_factoring,shor}.
+
+  Furthermore, when it comes to more concrete applications of Shor's algorithm,
+  a full-scale implementation of this algorithm to factor an $n$-bit number
+  may require up to $5n+1$ qubits for accurate results, and require 
+  on the order of $n^3$ operations~\cite{quantum_fac_efficient}.
 
@@
 
-  S. Whitlock, et al. present a method of SP factoring with Grover's
+  S. Whitlock, et al.\ present a method of SP factoring with Grover's
   algorithm. The implementation in their paper is highly optimized,
   and modifies the target value in their circuit from some semiprime $N$,
-  to $M$, a reduced number uniquely tied to $N$, which has prime factors
-  $p$ and $q$.
+  to $M$, a reduced number uniquely tied to $N$, which has unique factors 
+  $p$ and $q$ which can be used to calculate $a, b$, the prime factors of 
+  $N$. This optimization from $N$ to $M$ allows the implementation to ignore
+  the trivial prime factors $2$ and $3$, and requires fewer qubits than would
+  otherwise be needed to search for prime factors of $N$~\cite{quantum_factoring}.
 
   While this approach is admirable, it introduces a level of complexity 
-  that may hinder a learner's understanding of the mechanics at play,
-  so the implementation shown in section \ref{sec:Methodology} forgoes
+  that may hinder a learner's understanding of the mechanics at work,
+  so the implementation shown in section\ \ref{sec:Methodology} forgoes
   this abstraction from $N$ to $M$, and instead implements an oracle which
@@
 
-\section{Methodology} \label{sec:Methodology}
+\section{Methodology}\label{sec:Methodology}
+
+\begin{figure*}[!ht]\label{fig:FIGURA1}
+\centering
+% \includegraphics[width=7.9cm]{grover_inversion.png}
+\includegraphics[width=15.8cm]{grover_inversion.png}
+\caption{General circuit diagram for Grover's Algorithm, used to find 
+the inputs $x, y$ for which $f(x,y)=z$, for some known output $z$.}
+\end{figure*}
 
@@
 
-  Mention unitary matrices.
+  Operations can be performed on a set of input registers that start in uniform 
+  superposition, and these operations will affect each potential state individually. 
+  The properties of superposition are utilized by Grover's Oracle to selectively 
+  modify the states $|x,y\rangle$ in the input registers $R_x$ and $R_y$,
+  marking them as valid by setting them to $-|x,y\rangle$, only when the output register
+  $R_z$ matches some known search term $z$. An outline of a quantum circuit for
+  Grover's algorithm is seen in Figure~\ref{fig:FIGURA1}.
 
-  Describe how Grover's works and show figures of a generalized
-  circuit for Grover's to invert functions
+  The oracle in Grover's algorithm performs a controlled operation which is meant
+  to differentiate states $x,y$ that do result in the wanted target $z$ from 
+  states $x,y$ that do not result in the target $z$.
 
-  Reference figure 1.
-
-  Operations can be performed on a register in superposition, and these operations
-  will affect each potential state individually. This property is utilized by
-  Grover's Oracle to selectively target specific states which match the target
-  value, and the diffuser is used to increase the probability of measuring the
-  inputs which resulted in this marked target state.
-
-  \begin{figure}[h]
-  %\centering
-  \includegraphics[width=7.9cm]{grover_inversion.png}
-  \caption{General circuit diagram for Grover's Algorithm, used to find 
-  the inputs $x, y$ for which $f(x,y)=z$, for some known $z$.}
-  \label{FIGURA1}
+  \begin{figure}[h]\label{fig:FIGURA2}
+  \centering
+  \includegraphics[width=6.0cm]{oracle_15.png}
+  % \includegraphics[width=7.9cm]{oracle_15.png}
+  \caption{Example circuit diagram for Grover's oracle marking states of the input
+  registers $R_x$ and $R_y$ ($[q_0,q_2]$ and $[q_3,q_5]$, respectively) which
+  result in $z=15$.}
   \end{figure}
 
-  Include one figure showing the oracle, and one figure showing the diffuser.
+  Figure~\ref{fig:FIGURA2} shows an example of the oracle searching for the state $z=15$,
+  or rather, $R_z=|001111\rangle$. To implement a circuit which can selectively target
+  $z=15$, Toffoli gates (otherwise known as NOT, or X gates) are applied on 
+  $R_z[0]$ and $R_z[1]$, so that states where $R_z=|001111\rangle$ will temporarily be in
+  state $R_z=|111111\rangle$, and the multi-controlled Toffoli gates\cite{multi_toffoli}
+  will apply only for the desired states. These operations are then performed again,
+  returning all but the target qubit (which has the Z-gate applied) to their original
+  states.
+
+  \begin{figure}[h]\label{fig:FIGURA3}
+  \centering
+  % \includegraphics[width=7.9cm]{diffuse.png}
+  \includegraphics[width=5.0cm]{diffuse.png}
+  \caption{Example circuit diagram for a diffuser which amplifies the probability that
+  measurement will result in a state which has been marked by the oracle.
+  Input registers $R_x$ and $R_y$ (q0-q2 and q3-q5, respectively) after diffusion are 
+  more likely to be measured in a state such that $f(R_x,R_y)$ results in $R_z=|z\rangle$.}
+  \end{figure}
+
+  The diffuser in Grover's algorithm (Figure~\ref{fig:FIGURA3}) can then increase the 
+  probability of observing $-|x,y\rangle$ (states which have been marked by the oracle) 
+  through a process known as inversion about the mean.
 
@@
 
-  Describe our original approach- bitwise addition, registers, operations, etc.
+  As a proof of concept (prior to the release of~\cite{quantum_factoring}),
+  a function $f(x,y)=x+y$ is defined such that $R_x=|x\rangle$, $R_y=|y\rangle$,
+  and after performing $f(R_x,R_y)$, the output register $R_z$ shall be in the
+  state $|x+y\rangle$.
 
-  Mention why an alternative approach was needed.
+  This approach was implemented in a similar manner to a classical full-adder,
+  and worked on quantum simulators with $100\%$ accuracy~\cite{quantum_full_adder}.
 
-  Include a drawing of the circuit.
+  The semiclassical full-adder indeed works with Grover's algorithm, states were
+  filtered to only measure inputs which resulted in a sum matching some given value.
+  This is a trivial problem however, and only has potential usefulness due to the 
+  relationship between multiplication and addition.
+
+  Semiclassical arithmetic does have significant drawbacks, however. Despite
+  being relatively simple to implement due to the similarity with principles
+  that have a much broader range of documentation, the classical nature of this
+  implementation meant that in order to move to multiplication from this point,
+  the value of one register would need to be measured, and $R_x$ would then be
+  added to $R_z$ a number of times dependent on the value of $y$.
+
+  Measuring the state of either input register would collapse the superposition,
+  and break the underlying principles on which Grover's algorithm depends. Thus,
+  a different approach became necessary- one that could bridge the gap between 
+  addition and multiplication without needing to measure either register,
+  so that the operation can still work with inputs that are in superposition,
+  allowing the use of Grover's algorithm.
 
@@
 a and b from N.
-
-\balance
 
@@
 
+\balance
+
 \end{document}

### 2025-03-02 LaTeX/paper.tex
Defined iteration count

@@
   Grover's Algorithm is a quantum computing method 
-  that can be used to search a database in $O(\sqrt{n})$ time 
+  that can be used to search a database of $n$ values in $O(\sqrt{n})$ time 
   rather than the naive classical time complexity of $O(n)$\cite{grover}.
+
+  The exact number of iterations required varies on a case-by-case basis,
+  but is typically expressed as follows: in a search for one matching input
+  state, $\frac{\pi}{4}\sqrt{N}$ iterations are required, and in a search
+  for $k$ valid input states, $\sqrt{\pi}{4}\cdot \sqrt{\frac{N}{k}}$
+  iterations are required, where $N$ is the size of the search domain.
+
+  In most cases, $N=2^n$, where $n$ is the number of bits needed to represent
+  the target value. This is by no means a steadfast rule, and is meant as 
+  a helpful starting point for any confused readers attempting to implement
+  something similar themselves.
 

### 2025-03-03 LaTeX/paper.tex
Paper seems finished

@@
 \usepackage{graphicx}
+\usepackage{dblfloatfix}
 \begin{document}
@@
 \ \\ % leave an empty line between authors and affiliation
- $^1$ California State University, Chico, United States (note- full address at end of paper)}
+ $^1$ California State University, Chico, United States}
 
@@
 
-  In quantum computing, SP (semiprime) factoring is typically performed 
-  with Shor's algorithm, but it is possible to achieve the same results
-  more efficientily via Grover's algorithm\cite{quantum_factoring, grover}.
+  This paper details some of the first steps that our research group has
+  taken towards a practical demonstration of quantum advantage.
 
-  Key terms: Semiprime, superposition, entanglement, RSA encryption, (add more).
+  Grover's search algorithm can be leveraged to efficiently compute the inverse 
+  of many functions; this is addressed both from a general perspective, as well as
+  specific applications, including inversion of multiplication,
+  thereby finding the factors of semiprimes with greater efficiency 
+  than classical HPC methods and similar existing quantum algorithms.
 
-  The abstract with its heading should not be more than 100 mm long,
-  which is equivalent to 25 lines of text. Leave 2 line spaces at the
-  bottom of the abstract before continuing with the next heading.
+  RSA encryption relies on the fact that the multiplication of large
+  prime numbers is a trap-door function- computationally trivial to compute
+  the semiprime product, but classical methods of finding prime components
+  is so computationally expensive that it can be considered nearly impossible
+  at a large scale. This principle is the backbone of 
+  modern-day cybersecurity~\cite{FergusonSchneier2003}.
+
+  % In quantum computing, SP (semiprime) factoring is typically performed 
+  % with Shor's algorithm, but it is possible to achieve the same results
+  % more efficientily via Grover's algorithm\cite{quantum_factoring, grover}. 
+  %
+  \textbf{Key terms:} Semiprime, superposition, entanglement, Grover's algorithm, 
+  Shor's algorithm, quantum fourier transform, adjoint, RSA encryption, 
+  quantum advantage, RSA number, reversible function, trap-door function,
+  quantum circuit, scaling, parallel, CUDA, CUDA-Q, sieve, time complexity.
+  %
+  % The abstract with its heading should not be more than 100 mm long,
+  % which is equivalent to 25 lines of text. Leave 2 line spaces at the
+  % bottom of the abstract before continuing with the next heading.
 
@@
 The practicality of applied quantum computing is a topic of much debate,
-and there are not many examples of quantum computers being able to out-perform
-their classical counterpart, yet.
+and there are not yet many examples of quantum computers being able to out-perform
+their classical counterpart, a feat known as quantum advantage.
 
@@
 It is quite common to find code which implements a quantum algorithm like
-Grover's or Shor's, but very often these programs are hard-coded, and only
+Grover's\cite{grover} or Shor's\cite{shor}, but very often these 
+programs are hard-coded, and only
 work for a small handful of specific values\cite{shors_ibm}.
 
-Include a figure of our circuit diagram and briefly describe what it 
-does, and how it does it.
+This paper describes the generalized use of Grover's algorithm as the
+inverse of some function $F(x, y) = z$, with demonstrated applications
+inverting the arithmetic functions addition and multiplication. The 
+inverse of multiplication is a solution to prime factorization- a 
+non-trivial problem with significant implications for cybersecurity
+at a global scope.
+
+\begin{figure}[ht]\label{fig:FIGURA1}
+\centering
+\includegraphics[width=7.9cm]{grover_inversion.png}
+% \includegraphics[width=15.8cm]{grover_inversion.png}
+% \includegraphics[width=14cm]{grover_inversion.png}
+\caption{General circuit diagram for Grover's Algorithm, used to find 
+the inputs $x, y$ for which $f(x,y)=z$, for some known output $z$.}
+\end{figure}
+
+  \subsection{Goals}
+
+  The objective of this research is to clearly demonstrate quantum advantage 
+  by showing clear speed-up to solve the same problem at the same scale.
+
+  Some of the major limitations for applied quantum computing are 
+  the number of qubits required to perform a given task, the likelihood of errors
+  in measurement, and the overhead associated with running circuits on real-world
+  quantum computers.
+
+  % Today many functions are reversible with digital computing (while not adiabatic), 
+  % but not all. For example, a discrete cosine transformation or Fourier transform 
+  % can be reversed, but for other algorithms, the only option for reversal is 
+  % brute-force search or getting lucky. For example, optimizing a function can be 
+  % done by trial and error with Monte Carlo guessing, and the possible solutions can 
+  % be quickly tested for optimality, but many functions cannot be easily optimized 
+  % short of brute-force search or Monte Carlo. Other examples being considered by 
+  % our group include subset sums, path planning, and machine learning gradient descent.
+  %
+  While the semiprime factoring problem is just one algorithm where quantum circuits 
+  should have significant advantage over parallel factoring, 
+  the goal of this research is to concretely show that this particular problem is 
+  in fact a clear case of quantum advantage.
+
+  Furthermore, the longer-term goal is to identify the types of algorithms that 
+  likewise may have significant quantum advantage based upon reversible functions.
+
+  Grover's algorithm can be used to provide a very efficient search, 
+  which is in essence a content addressable memory that works at a scale limited only by qubit scaling.
+
+  One of the major intentions for this paper is demonstration of the broad utility of Grover's 
+  algorithm, and to provide a general reference
+  for how Grover's algorithm may be used to invert a given function.
 
@@
 
-  Why are we replicating the research, why is this important.
+  Semiprime factoring is an ideal problem for demonstrating quantum advantage,
+  as it is both challenging to compute classicaly, and has wide-reaching
+  impact if efficient solutions are found.
 
-  Quantum computers are a technology very much still under development. 
-  As such, one of the major limitations for applied quantum computing is 
-  the number of qubits required to perform a given task. If it can be verified 
-  that SP factoring with Grover's algorithm uses significantly less qubits than
-  Shor's, then the application of these techniques will be feasible far sooner.
+  Semiprime factoring is known to have a high time complexity due to the nature of
+  prime number generation with a sieve (filters out all non-primes) and trial division search.
+  This problem in particular becomes complex for large size semiprimes commonly used in 
+  encryption, which might be 4096 bits or more. 
+  Even a 128-bit semiprime, which is the product of two 64-bit primes requires time complexity
+  that is beyond polynomial, and therefore requires a parallel computer to solve today.
 
-  \subsection{Semiprime Factoring}
+  This is important since the simplicity of multiplying two large primes enables fast encryption of data, 
+  but the complexity of factoring semiprimes ensures privacy so that data can only be accessed by someone possessing a private key 
+  (one of the primes that compose the semiprime used for encryption).
 
-  What is SP factoring and why is it important. RSA, etc.
+  Data privacy hinges on this one-way function, called a trap-door, where factoring 
+  is beyond P complexity, but trivial if one possesses the required key.
 
-\section{Goals}
+  If a quantum computer makes SP factoring as simple as SP computation, given a 
+  reversible quantum circuit, then this means all encryption can potentially 
+  be broken by such a quantum circuit.
 
-The goal of this research endeavor is to estimate the problem scaling point
-at which some quantum algorithm may be able to out-perform our best classical
-solution to the same problem.
+  The only safety now for encryption is scaling the key size (semiprime) to keep 
+  it larger than the largest quantum computer number of qubits.
 
-Grover's algorithm has an incredibly wide range of potential use-cases,
-and an intention for this paper is to provide a generalized reference
-for how Grover's algorithm may be used to invert a given function.
+  For example, the RSA number 250, which is 892-bits long, was only recently factored using a parallel computer. 
+  The idea of factoring 4096 or bigger is nearly impossible even with the largest parallel computers available~\cite{FergusonSchneier2003}.
+
+  However, a quantum computer has a much lower time complexity if the number of qubits
+  can be scaled to implement a quantum circuit that can factor a semiprime. Ongoing research
+  at China State Key Laboratories suggests that they have been making significant
+  progress in breaking RSA encryption, considering their 48-bit demo using 10 qubits
+  in 2022~\cite{yan2022factoringintegerssublinearresources}. Furthermore, they claim
+  that with the techniques they have been using, it would be possible to break
+  RSA 2048 with a quantum circuit which needs only 372 qubits, far less than the
+  1,121 qubit machine currently available in the United 
+  States with IBM's Condor~\cite{abughanem2024ibmquantumcomputersevolution}.
+
+  The typical approach to semiprime factoring on a quantum computer is 
+  with Shor's algorithm, but there are many drawbacks to this approach,
+  and has not yet been observed to be practically advantageous.
+
+  If it can be verified that SP factoring with Grover's algorithm
+  uses significantly less qubits than Shor's, has less error, or has less overhead,
+  then the application of quantum semiprime factoring at a meaningful scale 
+  will be feasible far sooner.
 
@@
   Grover's Algorithm is a quantum computing method 
-  that can be used to search a database of $n$ values in $O(\sqrt{n})$ time 
-  rather than the naive classical time complexity of $O(n)$\cite{grover}.
+  that can be used to search a database of $N$ values in $O(\sqrt{N})$ time 
+  rather than the naive classical time complexity of $O(N)$\cite{grover}.
 
@@
 
-  S. Whitlock, et al.\ present a method of SP factoring with Grover's
+  S. Whitlock et al.\ present a method of SP factoring with Grover's
   algorithm. The implementation in their paper is highly optimized,
@@
   $p$ and $q$ which can be used to calculate $a, b$, the prime factors of 
-  $N$. This optimization from $N$ to $M$ allows the implementation to ignore
+  $N$~\cite{quantum_factoring}.
+
+  This optimization from $N$ to $M$ allows the implementation to ignore
   the trivial prime factors $2$ and $3$, and requires fewer qubits than would
-  otherwise be needed to search for prime factors of $N$~\cite{quantum_factoring}.
+  otherwise be needed to search for prime factors of $N$.
 
@@
 
-\begin{figure*}[!ht]\label{fig:FIGURA1}
-\centering
-% \includegraphics[width=7.9cm]{grover_inversion.png}
-\includegraphics[width=15.8cm]{grover_inversion.png}
-\caption{General circuit diagram for Grover's Algorithm, used to find 
-the inputs $x, y$ for which $f(x,y)=z$, for some known output $z$.}
-\end{figure*}
-
 Quantum algorithms take advantage of superposition and entanglement,
@@
 
-In a given register $R_n$ with $n$ qubits, values are represented in binary,
-such, for example, if some number $N=3$ were to be represented classically
-with $n=4$ bits, it might be seen in binary as $0011$, and on a qubit
-register that number may be represented similarly as $| 0011 \rangle$.
+% In a given register $R_n$ with $n$ qubits, values are represented in binary,
+% such, for example, if some number $N=3$ were to be represented classically
+% with $n=4$ bits, it might be seen in binary as $0011$, and on a qubit
+% register that number may be represented similarly as $| 0011 \rangle$.
+%
+  \subsection{The Use of Grover's Algorithm for General Function Inversion}
 
-  \subsection{Grover's Algorithm for General Function Inversion}
+  % Operations can be performed on a set of input registers that start in uniform 
+  % superposition, and these operations will affect each potential state individually. 
+  % The properties of superposition are utilized by Grover's Oracle to selectively 
+  % modify the states $|x,y\rangle$ in the input registers $R_x$ and $R_y$,
+  % marking them as valid by setting them to $-|x,y\rangle$, only when the output register
+  % $R_z$ matches some known search term $z$. An outline of a quantum circuit for
+  % Grover's algorithm is seen in Figure~\ref{fig:FIGURA1}.
+  %
+  The oracle in Grover's algorithm performs a controlled operation which is meant
+  to differentiate states $-|x,y\rangle$ that do result in the wanted target $z$ from 
+  states $|x,y\rangle$ that do not result in the target $|z\rangle$.
 
-  Operations can be performed on a set of input registers that start in uniform 
-  superposition, and these operations will affect each potential state individually. 
-  The properties of superposition are utilized by Grover's Oracle to selectively 
-  modify the states $|x,y\rangle$ in the input registers $R_x$ and $R_y$,
-  marking them as valid by setting them to $-|x,y\rangle$, only when the output register
-  $R_z$ matches some known search term $z$. An outline of a quantum circuit for
-  Grover's algorithm is seen in Figure~\ref{fig:FIGURA1}.
+  \begin{figure}[!ht]
+  \centering
+  % \includegraphics[width=6.0cm]{oracle_15.png}
+  \includegraphics[width=5.0cm]{oracle_15.png}
+  % \includegraphics[width=7.9cm]{oracle_15.png}
+  \caption{Example circuit diagram for Grover's oracle marking entangled states 
+  of the output register ($R_z=[q_0,q_{11}]$) via the target qubit ($q_{12}$), where
+  $R_z=|15\rangle$.}\label{fig:FIGURA2}
+  \end{figure}
 
-  The oracle in Grover's algorithm performs a controlled operation which is meant
-  to differentiate states $x,y$ that do result in the wanted target $z$ from 
-  states $x,y$ that do not result in the target $z$.
-
-  \begin{figure}[h]\label{fig:FIGURA2}
+  \begin{figure}[!h]
   \centering
-  \includegraphics[width=6.0cm]{oracle_15.png}
-  % \includegraphics[width=7.9cm]{oracle_15.png}
-  \caption{Example circuit diagram for Grover's oracle marking states of the input
-  registers $R_x$ and $R_y$ ($[q_0,q_2]$ and $[q_3,q_5]$, respectively) which
-  result in $z=15$.}
+  % \includegraphics[width=7.9cm]{diffuse.png}
+  % \includegraphics[width=5.0cm]{diffuse.png}
+  \includegraphics[width=4.2cm]{diffuse.png}
+  \caption{Example circuit diagram for a diffuser which amplifies the probability that
+  measurement will result in a state which has been marked by the oracle.
+  Input registers $R_x$ and $R_y$ ($[q_0,q_2]$ and $[q_3,q_5]$) are now 
+  more likely to be measured in a state such that $f(R_x,R_y)$ results in $R_z=|z\rangle$.}\label{fig:FIGURA3}
   \end{figure}
@@
   states.
-
-  \begin{figure}[h]\label{fig:FIGURA3}
-  \centering
-  % \includegraphics[width=7.9cm]{diffuse.png}
-  \includegraphics[width=5.0cm]{diffuse.png}
-  \caption{Example circuit diagram for a diffuser which amplifies the probability that
-  measurement will result in a state which has been marked by the oracle.
-  Input registers $R_x$ and $R_y$ (q0-q2 and q3-q5, respectively) after diffusion are 
-  more likely to be measured in a state such that $f(R_x,R_y)$ results in $R_z=|z\rangle$.}
-  \end{figure}
 
@@
   This approach was implemented in a similar manner to a classical full-adder,
-  and worked on quantum simulators with $100\%$ accuracy~\cite{quantum_full_adder}.
+  and has been observed to work in simulation with perfect accuracy~\cite{quantum_full_adder}.
 
-  The semiclassical full-adder indeed works with Grover's algorithm, states were
+  The semiclassical full-adder indeed works with Grover's algorithm. Input states were
   filtered to only measure inputs which resulted in a sum matching some given value.
@@
 
-  Semiclassical arithmetic does have significant drawbacks, however. Despite
-  being relatively simple to implement due to the similarity with principles
-  that have a much broader range of documentation, the classical nature of this
-  implementation meant that in order to move to multiplication from this point,
-  the value of one register would need to be measured, and $R_x$ would then be
-  added to $R_z$ a number of times dependent on the value of $y$.
+  Unfortunately, semiclassical multiplication requires direct measurement of $R_x$
+  or $R_y$, which would collapse the superposition, so a different approach was
+  needed.
 
-  Measuring the state of either input register would collapse the superposition,
-  and break the underlying principles on which Grover's algorithm depends. Thus,
-  a different approach became necessary- one that could bridge the gap between 
-  addition and multiplication without needing to measure either register,
-  so that the operation can still work with inputs that are in superposition,
-  allowing the use of Grover's algorithm.
+  % Semiclassical arithmetic does have significant drawbacks, however. Despite
+  % being relatively simple to implement due to the similarity with principles
+  % that have a much broader range of documentation, the classical nature of this
+  % implementation meant that in order to move to multiplication from this point,
+  % the value of one register would need to be measured, and $R_x$ would then be
+  % added to $R_z$ a number of times dependent on the value of $y$.
+  %
+  % Measuring the state of either input register would collapse the superposition,
+  % and break the underlying principles on which Grover's algorithm depends. Thus,
+  % a different approach became necessary- one that could bridge the gap between 
+  % addition and multiplication without needing to measure either register,
+  % so that the operation can still work with inputs that are in superposition,
+  % allowing the use of Grover's algorithm.
 
-  \subsection{Arithmetic in the Quantum Fourier Domain}
+  \subsection{Arithmetic in the Quantum Fourier Domain}\label{sec:qft_arithmetic}
 
-  Describe the updated methods of quantum arithmetic, and how it solved the 
-  previous problems.
+  The quantum fourier transform, QFT, is a very useful
+  operation, typically used to transform a qubit register from the
+  computational basis (binary) to the fourier basis (phase).  The QFT operation 
+  is defined in great detail by Perez et al.~\cite{quantum_arithmetic}.
 
-  Figures to visualize how the weighted phase shifts work to produce
-  expected results matching addition, scaled addition, and register 
-  multiplication.
+  To summarize, given a qubit register $R_x=|x\rangle$
+  with $n$ qubits in the computational basis, there are $d=2^n$ potential states $|k\rangle$
+  in $|x\rangle$ = $\{|0\rangle, |1\rangle, \ldots, |d-1\rangle\}$, the QFT operation in this
+  basis would be defined as:
+
+  \begin{equation}\label{eqn:QFT}
+    QFT|x\rangle = \frac{1}{\sqrt{d}} \sum_{k=0}^{d-1}e^{i{\frac{2\pi x k}{d}}}|k\rangle
+  \end{equation}
+
+  *It is worth noting that in some cases, a QFT on some $R_x$ may require a series of SWAP
+  operations $\{ SWP(q_0,q_{n-1}), SWP(q_1,q_{n-2}), \ldots, SWP(q_{\frac{n}{2}-1},q_{\frac{n}{2}})\}$
+  in order for future arithmetic to work as expected.
+
+  Once in the fourier basis, a specific number $x$ may be encoded by applying some
+  rotation $\omega_k$ to qubits $q_k \in R_x | q_k=R_x[k]$. The rotation $\omega_k$ applied
+  to each qubit $q_k$ can be defined as $\omega_k = \omega^{x k} = e^{i \frac{2\pi x k}{d}}$.
+
+  % The inverse QFT operation, IQFT, is simply the adjoint of QFT, and most 
+  % implementations allow you to automatically generate the adjoint of a given operation.
+  The inverse QFT operation, IQFT is used to return a qubit register $R_x$ from the fourier basis to the 
+  computational basis, retaining the values which have been mapped and operations
+  which have been applied to $R_x$.
+
+  Addition of two qubit registers $R_a$ in state $|a\rangle$ and $R_b$ in state 
+  $\phi(b)\rangle$ in the fourier basis 
+  ($\phi ADD(|a\rangle, |b\rangle)=|a + b\rangle$) may be performed by applying
+  controlled rotation gates $R_k$ which rotate qubits $b_j \in R_b$ by 
+  $\omega_j=e^\frac{2\pi i}{2^j}$ about the $z$-axis for each 
+  qubit $a_l | l \ge k, j=1+l-k$~\cite{quantum_arithmetic}.
+
+  Multiplication in the quantum fourier domain can be done similarly. In terms of
+  a quantum circuit generation implementation, simply treat the previously defined
+  addition method as a function which adds the value of one register to another,
+  and add some constant multiple $C$ as a parameter, adjusting $\omega_j$ to 
+  $\omega_{j,C}=e^{C\cdot \frac{2\pi i}{2^j}}$. Now, to send the product of the two values in $R_x$
+  and $R_y$ to $R_z$, do as follows: Add $|R_y|$ controlled $\phi ADD(R, q_c, C)$ gates to each
+  $q_x$ in $R_x$, which will add the value of $|C\cdot x\rangle$ to $R_z$ where $C=2^u$ for
+  each $q_u \in R_y \iff q_y = |1\rangle$. This is, in essence, performing repeated scaled addition from $R_x$ onto
+  $R_z$, but the scaling factor is the powers of two corresponding to qubits in $R_y$, which
+  in tandem is cumulatively equivalent to adding $|x\cdot y\rangle$ to $R_z$~\cite{quantum_arithmetic}.
+
+  \subsection{Semiprime Factoring with Grover's Algorithm}
+
+  After implementing the QFT arithmetic methods and the oracle and diffuser for
+  grover's, it is trivial to implement a SP factoring circuit. Our implementation
+  follows the diagram in Figure~\ref{fig:FIGURA1}, while substituting $F(x,y)$ for
+  the $\phi MULT(R_x, R_y)$ operation described at the end of section 
+  \ \ref{sec:qft_arithmetic}.
+
+  The only fine-tuning necessary here was to add additional bits to the $R_z$ register.
+  Typically, only $\lceil \log_2(N)\rceil$ qubits are needed to represent some number $N$,
+  and while that is true, we experienced something that might be considered quantum integer
+  overflow before increasing the number of qubits in $R_z$. Prime factors $a,b$ of $N$ may be as
+  little as one bit smaller than $N$, and due to the fact that $R_x$ and $R_y$ representing $a,b$
+  are in superposition, that meant that all numbers up to $2^{n-1}$ were being included
+  in the superposition for both $a$ and $b$, resulting in products far larger than could
+  be represented in $R_z$, which in turn led to false positives due to products that were
+  some sum of powers of 2 greater than $n$.
+
+  The temporary solution we found was to simply decrease the size of $R_x$ and $R_y$ to 
+  $\lceil \log_2(\frac{N}{3})\rceil$, and set the size of $R_z$ to double that, to ensure no
+  further overflow could occur.
+
+  % \subsection{Quantum Circuit Simulation}
+
+  % It can be very expensive and time-consuming to run quantum circuits on real-world
+  % quantum computers, especially for problems which require a large number of qubits.
+  % Simulation is a strong solution to this issue; the math involved with qubits
+  % is known, so the state of a quantum circuit can be tracked properly throughout 
+  % execution.
+
+  % The methods described in this paper have been programmed using CUDA-Q in C++. This
+  % method of simulation allows for generalized circuit generation algorithms, and
+  % the ability to verify that a solution theoretically works at larger problem scales
+  % than would be possible to attempt on an actual quantum computer given the current 
+  % limitations of the quantum computing industry.
 
@@
 
-Include some charts showing our runtime and qubit requirements vs N.
+To date, we have preliminary results based on CUDA-Q simulation of quantum circuits, 
+which have been compared to classic parallel methods to generate primes with a sieve 
+and search them for modulo zero factoring.
+
+This work is still in progress, but we have a working implementation of Grover's 
+algorithm with the CUDA-Q simulation which can estimate the time to factor any 
+semiprime up to the current scaling limits of the CUDA-Q simulation.
+
+We first plan to compare the Grover quantum circuit to our best parallel sieve 
+and modulo search with this scale-out with SDSC Expanse.
 
@@
 
-  How precise and accurate were our measurements. Mention edge-cases like
-  square semiprimes, etc.
+  On our CSU Chico A100 system, 
+  we have been able to scale this implementation up to a total of 32 qubits,
+  used to find the prime factors $47\times13=611$, where $611$ is a 10-bit semiprime. This
+  performance is due to the sub-optimality of the current implementation, as we have
+  not yet introduced the search-term reduction from $N$ to $M$ as is done by S. Whitlock 
+  et al.\cite{quantum_factoring}.
 
-  How many qubits were we able to simulate, i.e., how large of semiprimes
-  can we factor with our current systems.
+  Due to the exploratory nature of this work, the initially sub-optimal nature of our 
+  implementation is intentional, because it allows for a more direct view of the inputs
+  and outputs in our circuit.
 
-  \subsection{Comparison to Shor's Algorithm}
+  For context, our current implementation uses $4 \lceil \log_2(\frac{N}{3})\rceil$ qubits
+  to find the prime factors of an $n$-bit semiprime, whereas the design by S. Whitlock 
+  et al.\cite{quantum_factoring} uses up to $2n-5$ qubits, which allowed them to simulate circuits which found
+  prime factors of up to $35$-bit semiprimes, using up to a total of $65$ qubits. 
+  The limiting factor for our simulations is VRAM, so it is expected that after implementing 
+  the optimizations from S. Whitlock et al.,\ our simulations should be able to scale up to 
+  $18$-bit semiprimes on the current equipment.
 
-  List strengths and weaknesses of Shor's, i.e., more documentation, more
-  examples, larger code base to reference, but ours is faster and uses less
-  qubits.
+  % In simulation, our implementation of quantum semiprime factoring with Grover's algorithm
+  % has $100\%$ accuracy on all observed simulation runs with 100 shots each. The expected
+  % accuracy is very near $100\%$, and simulating with a greater number of shots might allow us
+  % to see a handful of the expected erronious results, but the simulations are rather time 
+  % consuming (finding prime factors of 611 took over 20 minutes on the current machine), 
+  % and the current priority is verification of a working circuit, which has indeed been observed.
+  %
+\section{Conclusion}
 
-\section{Conclusion}
+\balance
 
@@
 
-Implementation of the optimization with M, S, p, and q, rather than just 
-a and b from N.
+The current priority regarding the quantum circuit is to implement the optimizations
+mentioned by S. Whitlock et al.\ to substitute the search term $N$ with the smaller
+search term $M$, which should reduce the number of qubits needed from 
+$4 \lceil \log_2(\frac{N}{3})\rceil$ to $2n-5$.
+
+We have recently gained access to resources at the San Diego Supercomputing 
+Center (SDSC) Expanse cluster via an NSF allocation grant. This equipment will allow us to
+simulate on far larger problem scales, and by tracking the number of operations (quantum gates)
+used at different problem scales and comparing those counts against the number of operations
+performed in our classical parallel solution, we should be able to simulate circuits at a scale
+much larger than our current limitation of $\approx 32$ qubits.
 
@@
 % 
-Acknowledge the source paper.
+Jacob Collins has been funded by Chico State Enterprises as an undergraduate research assistant
+through funding provided by the Department of Energy via a grant titled: \textit{QIST in the CSU:\ 
+Expanding Access to Quantum Information Science and Technology.}
 
@@
 
-\balance
-
 \end{document}

### 2025-03-03 LaTeX/paper.tex
Fin.

@@
 
-  The typical approach to semiprime factoring on a quantum computer is 
-  with Shor's algorithm, but there are many drawbacks to this approach,
-  and has not yet been observed to be practically advantageous.
+  % The typical approach to semiprime factoring on a quantum computer is 
+  % with Shor's algorithm, but there are many drawbacks to this approach,
+  % and has not yet been observed to be practically advantageous.
 
@@
   % Grover's algorithm is seen in Figure~\ref{fig:FIGURA1}.
-  %
+
+  This use of Grover's algorithm involves three main parts: some function with
+  one or multiple inputs, the oracle which filters for states in which the
+  desired output was observed, and the diffuser, which increases the probability 
+  of observing inputs from the correct state. An overview of this circuit is
+  shown in Figure~\ref{fig:FIGURA1}.
+
   The oracle in Grover's algorithm performs a controlled operation which is meant
@@
 
-What have we learned so far, what does it mean, at what problem scale might
-we see quantum advantage based on our results, etc.
+Grover's algorithm has been demonstrated to be a highly versatile function,
+able to invert almost any function that can be implemented on a quantum 
+computer with inputs in superposition.
+
+Quantum methods of SP factoring have been developing at a quick pace,
+and it will most likely not be very long before practical examples
+of quantum advantage may be seen.
 
@@
 Jacob Collins has been funded by Chico State Enterprises as an undergraduate research assistant
-through funding provided by the Department of Energy via a grant titled: \textit{QIST in the CSU:\ 
+through funding provided by the Department of Energy via a grant titled: \emph{QIST in the CSU:\ 
 Expanding Access to Quantum Information Science and Technology.}

### 2025-03-03 LaTeX/paper.tex
Fixed my address lol
Updated reference

@@
 
-  Some of the major limitations for applied quantum computing are 
-  the number of qubits required to perform a given task, the likelihood of errors
-  in measurement, and the overhead associated with running circuits on real-world
-  quantum computers.
+  % Some of the major limitations for applied quantum computing are 
+  % the number of qubits required to perform a given task, the likelihood of errors
+  % in measurement, and the overhead associated with running circuits on real-world
+  % quantum computers.
 
@@
 
+  One of the major intentions for this paper is demonstration of the broad utility of Grover's 
+  algorithm.%, and to provide a general reference
+  %for how Grover's algorithm may be used to invert a given function.
+
   Furthermore, the longer-term goal is to identify the types of algorithms that 
   likewise may have significant quantum advantage based upon reversible functions.
-
-  Grover's algorithm can be used to provide a very efficient search, 
-  which is in essence a content addressable memory that works at a scale limited only by qubit scaling.
-
-  One of the major intentions for this paper is demonstration of the broad utility of Grover's 
-  algorithm, and to provide a general reference
-  for how Grover's algorithm may be used to invert a given function.
+  % Grover's algorithm can be used to provide a very efficient search, 
+  % which is in essence a content addressable memory that works at a scale limited only by qubit scaling.
 
@@
 
-  If a quantum computer makes SP factoring as simple as SP computation, given a 
-  reversible quantum circuit, then this means all encryption can potentially 
-  be broken by such a quantum circuit.
+  % If a quantum computer makes SP factoring as simple as SP computation, given a 
+  % reversible quantum circuit, then this means all encryption can potentially 
+  % be broken by such a quantum circuit.
 
@@
 
-  For example, the RSA number 250, which is 892-bits long, was only recently factored using a parallel computer. 
+  For example, the RSA number 250, which is 892-bits long, was only recently 
+  factored using a parallel computer with the best known SP factoring 
+  method known right now~\cite{Bai2016}.
+
   The idea of factoring 4096 or bigger is nearly impossible even with the largest parallel computers available~\cite{FergusonSchneier2003}.
@@
   progress in breaking RSA encryption, considering their 48-bit demo using 10 qubits
-  in 2022~\cite{yan2022factoringintegerssublinearresources}. Furthermore, they claim
+  in 2022~\cite{yan2022factoringintegerssublinearresources}.
+
+  Furthermore, they claim
   that with the techniques they have been using, it would be possible to break
@@
 Jacob Collins\\
-1565 Filbert Ave\\
+1565 Filbert Avenue, Chico, CA 95926\\
 jbcollins@csuchico.edu

### 2025-03-27 SP-factoring/simple_factor.cpp
Clean up

@@ -2,10 +2,6 @@
  * Description: 
  *      Using grover's algorithm to invert QFT multiplication
  *      to achieve quantum SP factoring.
- * Note:
- *      Must be updated with methods from [this paper](https://arxiv.org/pdf/2312.10054)
- *      to reduce error and increase qubit efficiency.
- *      ^ IP in `factor.cpp`
  * Author: Jacob Collins
  **********************************/
 
@@ -165,8 +161,6 @@ __qpu__ void setInt(const long val, cudaq::qview<> qs, bool qorder=true) {
   }
 }
 
-// Converted from qml function
-// https://docs.pennylane.ai/en/stable/_modules/pennylane/templates/subroutines/qft.html#QFT
 __qpu__ void quantumFourierTransform(cudaq::qview<> qs) {
   const int nbits = qs.size();
   int shift_len = nbits-1;
@@ -245,10 +239,8 @@ __qpu__ void oracle(cudaq::qview<> ctrl, cudaq::qview<> tgt, const long target_s
   }
 }
 
-// Based on pennylane.ai implementation
 __qpu__ void QFTMult(cudaq::qview<> x_reg, cudaq::qview<> y_reg, cudaq::qview<> z_reg) {
   const int nbits_x = x_reg.size();
-  // const int nbits_z = z_reg.size();
   int c;
 
   quantumFourierTransform(z_reg);

### 2025-03-27 LaTeX/paper.tex
Update citation

@@
 algorithm with the CUDA-Q simulation which can estimate the time to factor any 
-semiprime up to the current scaling limits of the CUDA-Q simulation.
+semiprime up to the current scaling limits of the CUDA-Q simulation\cite{quantumfactoring_github}.
 

### 2025-03-28 SP-factoring/factor.cpp
Update comments

@@ -413,7 +413,7 @@ void run_SP_factor(long N) {
   auto end = std::chrono::high_resolution_clock::now();
   auto duration =
       std::chrono::duration_cast<std::chrono::nanoseconds>(end - start).count();
-  printf("\nAdder finished in %s.\n", format_time(duration).c_str());
+  printf("\nCircuit finished in %s.\n", format_time(duration).c_str());
   std::vector<std::tuple<std::string, size_t>> results = sort_map(counts.to_map());
   printf("\nMEASURED RESULTS\n");
   display_full_results(results, N, nbits_x, nbits_y, nbits_z, NUM_RESULTS_DISPLAYED);
@@ -424,6 +424,7 @@ void run_SP_factor(long N) {
 int main(int argc, char *argv[]) {
   // PARSE INPUT VALUES
   // Default search value
+  printf("This file is WIP, use simple_factor.cpp for testing.\n");
   printf("Usage: ./factor.x [N = Semiprime]\n");
   long N = 15;
   if (argc >= 2) {

### 2025-03-28 SP-factoring/simple_factor.cpp

@@ -2,7 +2,13 @@
  * Description: 
  *      Using grover's algorithm to invert QFT multiplication
  *      to achieve quantum SP factoring.
+ *
  * Author: Jacob Collins
+ *
+ * Note: 
+ *    CURRENTLY FUNCTIONAL
+ *    Uses ~4n qubits instead of the optimal ~2n.
+ *    WIP optimized factorization in factor.cpp
  **********************************/
 
 #include <cudaq.h>

### 2025-03-28 SP-factoring/simple_factor.cpp
Update input verification

@@ -395,6 +395,8 @@ int main(int argc, char *argv[]) {
   printf("Finding prime factors of %ld\n", z);
 
   if (z < 9 || z % 2 == 0) { printf("Invalid input for z\n"); }
-
+  if (sqrt(z) == (int) sqrt(z)) { 
+    printf("Invalid SP: square semiprime is trivial.\n");
+  }
   run_SP_factor(z);
 }

### 2025-03-28 SP-factoring/simple_factor.cpp
Input validation

@@ -397,6 +397,7 @@ int main(int argc, char *argv[]) {
   if (z < 9 || z % 2 == 0) { printf("Invalid input for z\n"); }
   if (sqrt(z) == (int) sqrt(z)) { 
     printf("Invalid SP: square semiprime is trivial.\n");
+    exit(EXIT_FAILURE);
   }
   run_SP_factor(z);
 }

### 2025-03-29 SP-factoring/simple_factor.cpp
Update output

@@ -358,6 +358,7 @@ void run_SP_factor(long z) {
 
   printf("\nVERIFIED INPUTS\n");
   printf("N: %ld (%s)\n", z, bin_str(z, nbits_z).c_str());
+  printf("Circuit requires %d qubits.\n", nbits_y + nbits_x + nbits_z + 1);
 
   // Draw circuit and view statevector
   if (ENABLE_CIRCUIT_FIG)
@@ -387,7 +388,7 @@ void run_SP_factor(long z) {
 int main(int argc, char *argv[]) {
   // PARSE INPUT VALUES
   // Default search value
-  printf("Usage: ./simple_factor.x [N = Semiprime]\n");
+  printf("Usage: ./simple_factor.x [N]\n");
   long z = 15;
   if (argc >= 2) {
     z = strtol(argv[1], nullptr, 10);

### 2025-03-29 SP-factoring/run_mpi.sh
Reorganized sp dir

@@ -1,0 +1,23 @@
+#!/bin/bash
+
+##########################
+#This part was generated by ChatGPT
+# Check if nvidia-smi is available
+if ! command -v nvidia-smi &> /dev/null; then
+    echo "nvidia-smi not found. NVIDIA drivers may not be installed or no NVIDIA GPUs are available."
+    exit 1
+fi
+# Use nvidia-smi to list GPUs and count the number of lines in the output
+gpu_count=$(nvidia-smi --query-gpu=name --format=csv,noheader | wc -l)
+##########################
+
+
+if [ "$#" -eq 0 ]; then
+  argument=77
+else
+  argument=$0
+fi
+
+
+nvq++ simple_factor.cpp --target nvidia --target-option mgpu
+mpiexec -np $gpu_count ./a.out $argument

### 2025-03-29 SP-factoring/simple_factor.cpp

@@ -29,8 +29,8 @@
 #define ENABLE_MISC_DEBUG false
 #define ENABLE_STATEVECTOR false
 
-//#define NUMBER_OF_SHOTS 100
-#define NUMBER_OF_SHOTS 1
+#define NUMBER_OF_SHOTS 100
+// #define NUMBER_OF_SHOTS 1
 #define NUM_RESULTS_DISPLAYED 5
 
 /**************************************************

### 2025-03-29 SP-factoring/tools/check_gpu_count.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+# Generated by ChatGPT
+
+# Check if nvidia-smi is available
+if ! command -v nvidia-smi &> /dev/null; then
+    echo "nvidia-smi not found. NVIDIA drivers may not be installed or no NVIDIA GPUs are available."
+    exit 1
+fi
+
+# Use nvidia-smi to list GPUs and count the number of lines in the output
+gpu_count=$(nvidia-smi --query-gpu=name --format=csv,noheader | wc -l)
+
+echo "Number of available GPUs: $gpu_count"

### 2025-03-29 SP-factoring/run_mpi.sh
Added mpi_run gpu script

@@ -9,15 +9,23 @@ if ! command -v nvidia-smi &> /dev/null; then
 fi
 # Use nvidia-smi to list GPUs and count the number of lines in the output
 gpu_count=$(nvidia-smi --query-gpu=name --format=csv,noheader | wc -l)
+echo "Running with $gpu_count GPU(s)."
 ##########################
-
 
 if [ "$#" -eq 0 ]; then
   argument=77
+  echo "Warning: No argument given!"
 else
-  argument=$0
+  argument="$1"
 fi
 
-
+echo "Compiling circuit..."
 nvq++ simple_factor.cpp --target nvidia --target-option mgpu
-mpiexec -np $gpu_count ./a.out $argument
+
+echo "Finding prime factors of $argument."
+
+OUTPUT_FILE="output/test_$1.txt"
+
+mpiexec -np $gpu_count ./a.out "$argument" > "$OUTPUT_FILE" &
+
+echo "Job Completed."

### 2025-03-29 SP-factoring/simple_factor.cpp
MPI enabled

@@ -372,6 +372,7 @@ void run_SP_factor(long z) {
   auto start = std::chrono::high_resolution_clock::now();
 
   int n_shots = NUMBER_OF_SHOTS; // Get a lot of samples
+  cudaq::set_target("nvidia", "mqpu");
   auto counts = cudaq::sample(n_shots, runFactorization{}, z, nbits_x, nbits_y, nbits_z);
 
   auto end = std::chrono::high_resolution_clock::now();
@@ -388,6 +389,8 @@ void run_SP_factor(long z) {
 int main(int argc, char *argv[]) {
   // PARSE INPUT VALUES
   // Default search value
+  cudaq::mpi::initialize(argc, argv);
+  
   printf("Usage: ./simple_factor.x [N]\n");
   long z = 15;
   if (argc >= 2) {
@@ -401,4 +404,5 @@ int main(int argc, char *argv[]) {
     exit(EXIT_FAILURE);
   }
   run_SP_factor(z);
+  cudaq::mpi::finalize();
 }

### 2025-03-29 SP-factoring/simple_factor.cpp
Update on expanse

@@ -372,7 +372,7 @@ void run_SP_factor(long z) {
   auto start = std::chrono::high_resolution_clock::now();
 
   int n_shots = NUMBER_OF_SHOTS; // Get a lot of samples
-  cudaq::set_target("nvidia", "mqpu");
+//  set_target("nvidia", "mgpu");
   auto counts = cudaq::sample(n_shots, runFactorization{}, z, nbits_x, nbits_y, nbits_z);
 
   auto end = std::chrono::high_resolution_clock::now();
@@ -389,7 +389,6 @@ void run_SP_factor(long z) {
 int main(int argc, char *argv[]) {
   // PARSE INPUT VALUES
   // Default search value
-  cudaq::mpi::initialize(argc, argv);
   
   printf("Usage: ./simple_factor.x [N]\n");
   long z = 15;
@@ -403,6 +402,7 @@ int main(int argc, char *argv[]) {
     printf("Invalid SP: square semiprime is trivial.\n");
     exit(EXIT_FAILURE);
   }
+  cudaq::mpi::initialize(argc, argv);
   run_SP_factor(z);
   cudaq::mpi::finalize();
 }

### 2025-03-30 SP-factoring/simple_factor.cpp
Update

@@ -402,7 +402,7 @@ int main(int argc, char *argv[]) {
     printf("Invalid SP: square semiprime is trivial.\n");
     exit(EXIT_FAILURE);
   }
-  cudaq::mpi::initialize(argc, argv);
+//  cudaq::mpi::initialize(argc, argv);
   run_SP_factor(z);
-  cudaq::mpi::finalize();
+//  cudaq::mpi::finalize();
 }

### 2025-03-30 LaTeX/paper.tex
Formatting for arxiv
Add notes for adjustment

@@
 \usepackage{dblfloatfix}
+\usepackage{url}
 \begin{document}
@@
   or rather, $R_z=|001111\rangle$. To implement a circuit which can selectively target
-  $z=15$, Toffoli gates (otherwise known as NOT, or X gates) are applied on 
-  $R_z[0]$ and $R_z[1]$, so that states where $R_z=|001111\rangle$ will temporarily be in
+  $z=15$, Toffoli gates (controlled-NOT) are applied on $R_z[0]$ and $R_z[1]$, 
+  so that states where $R_z=|001111\rangle$ will temporarily be in
   state $R_z=|111111\rangle$, and the multi-controlled Toffoli gates\cite{multi_toffoli}

### 2025-03-31 LaTeX/paper.tex
Update paper, brief
Update paper

@@
 inverse of some function $F(x, y) = z$, with demonstrated applications
-inverting the arithmetic functions addition and multiplication. The 
-inverse of multiplication is a solution to prime factorization- a 
-non-trivial problem with significant implications for cybersecurity
-at a global scope.
+inverting the arithmetic functions addition and multiplication. Specifically,
+our implementation can generate and simulate a circuit to find the distinct prime
+factors of any given semiprime.
 
@@
   state $R_z=|111111\rangle$, and the multi-controlled Toffoli gates\cite{multi_toffoli}
-  will apply only for the desired states. These operations are then performed again,
-  returning all but the target qubit (which has the Z-gate applied) to their original
-  states.
+  will apply a NOT operation to the target qubit only for the desired states (where $z=15$). 
+  These operations are then performed again, returning all but the target qubit 
+  (which has the Z-gate applied) to their original states.
 

### 2025-03-31 SP-factoring/simple_factor.cpp

@@ -25,7 +25,7 @@
 #include <vector>
 
 #define ENABLE_DEBUG true // Displays full bitwise output
-#define ENABLE_CIRCUIT_FIG false
+#define ENABLE_CIRCUIT_FIG true
 #define ENABLE_MISC_DEBUG false
 #define ENABLE_STATEVECTOR false
 

### 2025-03-31 SP-factoring/simple_factor.cpp
Update example figure

@@ -25,7 +25,7 @@
 #include <vector>
 
 #define ENABLE_DEBUG true // Displays full bitwise output
-#define ENABLE_CIRCUIT_FIG true
+#define ENABLE_CIRCUIT_FIG false
 #define ENABLE_MISC_DEBUG false
 #define ENABLE_STATEVECTOR false
 

### 2025-03-31 generate_drawings/generate_drawings.cpp
Generate fig for oracle

@@ -277,8 +277,8 @@ struct runFactorization {
     cudaq::qvector tgt(1);
     // h(x_reg);
     // h(y_reg);
-    // oracle(z_reg, tgt.front(1), semiprime);
-    reflect_uniform(q_reg.front(nbits_x+nbits_y), tgt.front(1));
+    oracle(z_reg, tgt.front(1), semiprime);
+//    reflect_uniform(q_reg.front(nbits_x+nbits_y), tgt.front(1));
 
     // Wikipedia: ( pi / 4 ) * sqrt( N / k )
     // N: Size of search space (2^n choose 2)

### 2025-04-13 LaTeX/paper.tex
Paper revised

@@
 
-  The objective of this research is to clearly demonstrate quantum advantage 
+  The greater objective of this research is to clearly demonstrate quantum advantage 
   by showing clear speed-up to solve the same problem at the same scale.
@@
 
-  One of the major intentions for this paper is demonstration of the broad utility of Grover's 
-  algorithm.%, and to provide a general reference
+  One major intention for this paper in particular is demonstration of the broad 
+  utility of Grover's algorithm. %, and to provide a general reference
   %for how Grover's algorithm may be used to invert a given function.
-
-  Furthermore, the longer-term goal is to identify the types of algorithms that 
+  Furthermore, another long-term goal of this research is to identify the types of algorithms that 
   likewise may have significant quantum advantage based upon reversible functions.
@@
   encryption, which might be 4096 bits or more. 
-  Even a 128-bit semiprime, which is the product of two 64-bit primes requires time complexity
-  that is beyond polynomial, and therefore requires a parallel computer to solve today.
+  % Even a 128-bit semiprime, which is the product of two 64-bit primes requires time complexity
+  % that is beyond polynomial, and therefore requires a parallel computer to solve today.
 
-  This is important since the simplicity of multiplying two large primes enables fast encryption of data, 
-  but the complexity of factoring semiprimes ensures privacy so that data can only be accessed by someone possessing a private key 
-  (one of the primes that compose the semiprime used for encryption).
+  % This is important since the simplicity of multiplying two large primes enables fast encryption of data, 
+  % but the complexity of factoring semiprimes ensures privacy so that data can only be accessed by someone possessing a private key 
+  % (one of the primes that compose the semiprime used for encryption).
 
-  Data privacy hinges on this one-way function, called a trap-door, where factoring 
-  is beyond P complexity, but trivial if one possesses the required key.
+  % Data privacy hinges on this one-way function, called a trap-door, where factoring 
+  % is beyond P complexity, but trivial if one possesses the required key.
 
@@
 
-  The only safety now for encryption is scaling the key size (semiprime) to keep 
-  it larger than the largest quantum computer number of qubits.
+  % The only safety now for encryption is scaling the key size (semiprime) to keep 
+  % it larger than the largest quantum computer number of qubits.
 
@@
 
-  The idea of factoring 4096 or bigger is nearly impossible even with the largest parallel computers available~\cite{FergusonSchneier2003}.
+  % The idea of factoring 4096 or bigger is nearly impossible even with the largest parallel computers available~\cite{FergusonSchneier2003}.
 
@@
 
+  The two most significant limitations to applied quantum computing are 
+  qubit count and error rate. The algorithm displayed in this paper (and also by
+  S. Whitlock, et al.~\cite{quantum_factoring}) demonstrates
+  significant optimizations regarding the number of qubits required for semiprime
+  factoring. It is important to note, however, that error rate increases dramatically
+  in proportion to the number of gates applied, which may reduce the viability of
+  these algorithms in practice. That being said, there are emerging quantum computing 
+  hardware solutions which claim to have far better error-control methods than have yet
+  been observed, such as the Majorana I~\cite{Aghaee2025}.
+
   If it can be verified that SP factoring with Grover's algorithm
@@
   then the application of quantum semiprime factoring at a meaningful scale 
-  will be feasible far sooner.
+  may be feasible far sooner.
 
@@
   but is typically expressed as follows: in a search for one matching input
-  state, $\frac{\pi}{4}\sqrt{N}$ iterations are required, and in a search
-  for $k$ valid input states, $\sqrt{\pi}{4}\cdot \sqrt{\frac{N}{k}}$
-  iterations are required, where $N$ is the size of the search domain.
+  state, $\frac{\pi }{4}\sqrt{N}$ iterations are required, and in a search
+  for $2$ valid input states, $\lfloor \frac{\pi }{4} \cdot 2^\frac{n_x + n_y}{2}\rfloor$
+  iterations are required, where $N$ is the size of the search domain, and $n_x, n_y$ are
+  the number of qubits needed to represent the prime factors $x$ and $y$, respectively~\cite{quantum_factoring}.
 
-  In most cases, $N=2^n$, where $n$ is the number of bits needed to represent
-  the target value. This is by no means a steadfast rule, and is meant as 
-  a helpful starting point for any confused readers attempting to implement
-  something similar themselves.
+  % In most cases, $N=2^n$, where $n$ is the number of bits needed to represent
+  % the target value. This is by no means a steadfast rule, and is meant as 
+  % a helpful starting point for any confused readers attempting to implement
+  % something similar themselves.
 
@@
   Shor's algorithm is the most well-known approach to prime factorization
-  in quantum computing. However, there are many drawbacks to this approach,
-  the most notable of which being the need to take measurements mid-circuit
-  and essentially re-run with new values afterwards, which introduces a 
-  significant amount of overhead. Even recently improved versions of Shor's
-  algorithm still require a minimum of $2n+1$ qubits, and tend to be 
-  extremely sensitive to noise, which leads to high error\cite{quantum_factoring,shor}.
-
-  Furthermore, when it comes to more concrete applications of Shor's algorithm,
-  a full-scale implementation of this algorithm to factor an $n$-bit number
-  may require up to $5n+1$ qubits for accurate results, and require 
-  on the order of $n^3$ operations~\cite{quantum_fac_efficient}.
+  in quantum computing. While it is the fastest known quantum algorithm for 
+  factoring semiprimes, it requires (in most cases) $5n+1$ qubits~\cite{quantum_fac_efficient},
+  which is too large for problems of a practical size~\cite{quantum_factoring,shor}.
 
@@
 
-  This optimization from $N$ to $M$ allows the implementation to ignore
-  the trivial prime factors $2$ and $3$, and requires fewer qubits than would
-  otherwise be needed to search for prime factors of $N$.
+  % This optimization from $N$ to $M$ allows the implementation to ignore
+  % the trivial prime factors $2$ and $3$, and requires fewer qubits than would
+  % otherwise be needed to search for prime factors of $N$.
 
@@
   this abstraction from $N$ to $M$, and instead implements an oracle which
-  searches directly for prime factors $a$ and $b$ of a semiprime $N$.
+  searches directly for prime factors $a$ and $b$ of a semiprime $N$, without
+  the additional pre-processing and post-processing steps.
 
@@
   This use of Grover's algorithm involves three main parts: some function with
-  one or multiple inputs, the oracle which filters for states in which the
+  one or multiple inputs ($F(x,y)$ and $F^{\dagger}(x,y)$), the oracle which filters for states in which the
   desired output was observed, and the diffuser, which increases the probability 
-  of observing inputs from the correct state. An overview of this circuit is
-  shown in Figure~\ref{fig:FIGURA1}.
+  of observing inputs which match the previously marked state. An overview of this circuit is
+  shown in Figure~\ref{fig:FIGURA1}. The $H$ operations on $R_x$ and $R_y$ are
+  simply Hadamard operations, placing both registers in a uniform superposition.
 
@@
   to differentiate states $-|x,y\rangle$ that do result in the wanted target $z$ from 
-  states $|x,y\rangle$ that do not result in the target $|z\rangle$.
+  states $|x,y\rangle$ that do not result in the target $|z\rangle$ by conditionally 
+  flipping the phase of the target qubit.
 
@@
   \caption{Example circuit diagram for Grover's oracle marking entangled states 
-  of the output register ($R_z=[q_0,q_{11}]$) via the target qubit ($q_{12}$), where
-  $R_z=|15\rangle$.}\label{fig:FIGURA2}
+  of the output register ($R_z=[q_6,q_{11}]$) via the target qubit ($q_{12}$), where
+  $R_z=|15\rangle = |001111\rangle$.}\label{fig:FIGURA2}
   \end{figure}
@@
   or rather, $R_z=|001111\rangle$. To implement a circuit which can selectively target
-  $z=15$, Toffoli gates (controlled-NOT) are applied on $R_z[0]$ and $R_z[1]$, 
-  so that states where $R_z=|001111\rangle$ will temporarily be in
-  state $R_z=|111111\rangle$, and the multi-controlled Toffoli gates\cite{multi_toffoli}
-  will apply a NOT operation to the target qubit only for the desired states (where $z=15$). 
-  These operations are then performed again, returning all but the target qubit 
-  (which has the Z-gate applied) to their original states.
+  $z=15$, NOT gates are applied on $R_z[0]$ and $R_z[1]$ (seen in the figure as $q_6,q_7$), 
+  so that states where $R_z=|001111\rangle$ will then be in the
+  state $R_z=|111111\rangle$, and the multi-qubit Toffoli gates\cite{multi_toffoli}
+  will apply a NOT operation to the target qubit only for the desired states where $z=15$. 
+  % $q_6$ and $q_7$ are chosen in particular because they are the $|0\rangle$ qubits in
+  % the bitwise representation of $15$, and for the multi-qubit Toffoli to select this state,
+  % all control qubits must be in state $|1\rangle$. 
+  The NOT gates are again applied to $R_z$, returning it to state $|001111\rangle$,
+  while the target qubit retains the phase flip in those corresponding states.
+
+  To clarify, Toffoli gates have a target qubit (Seen as $q_{12}$ in Figure~\ref{fig:FIGURA2}, and `Tgt' in Figure~\ref{fig:FIGURA1}) 
+  and two control qubits which must both be in state $|1\rangle$ for a NOT operation to be applied
+  to the target qubit. There are methods of combining multiple Toffoli gates to behave
+  as a multi-qubit Toffoli gate, which behaves similarly, but can have any number of control qubits ($[q_6,q_{11}]$),
+  instead of being limited to just two\cite{multi_toffoli}.
 
@@
   probability of observing $-|x,y\rangle$ (states which have been marked by the oracle) 
-  through a process known as inversion about the mean.
+  through a process known as inversion about the mean~\cite{grover}.
 
-  \subsection{Semiclassical Arithmetic}
+  % \subsection{Semiclassical Arithmetic}
 
-  As a proof of concept (prior to the release of~\cite{quantum_factoring}),
-  a function $f(x,y)=x+y$ is defined such that $R_x=|x\rangle$, $R_y=|y\rangle$,
-  and after performing $f(R_x,R_y)$, the output register $R_z$ shall be in the
-  state $|x+y\rangle$.
+  % As a proof of concept (prior to the release of~\cite{quantum_factoring}),
+  % a function $f(x,y)=x+y$ is defined such that $R_x=|x\rangle$, $R_y=|y\rangle$,
+  % and after performing $f(R_x,R_y)$, the output register $R_z$ shall be in the
+  % state $|x+y\rangle$.
 
-  This approach was implemented in a similar manner to a classical full-adder,
-  and has been observed to work in simulation with perfect accuracy~\cite{quantum_full_adder}.
+  % This approach was implemented in a similar manner to a classical full-adder,
+  % and has been observed to work in simulation with perfect accuracy~\cite{quantum_full_adder}.
 
-  The semiclassical full-adder indeed works with Grover's algorithm. Input states were
-  filtered to only measure inputs which resulted in a sum matching some given value.
-  This is a trivial problem however, and only has potential usefulness due to the 
-  relationship between multiplication and addition.
+  % The semiclassical full-adder indeed works with Grover's algorithm. Input states were
+  % filtered to only measure inputs which resulted in a sum matching some given value.
+  % This is a trivial problem however, and only has potential usefulness due to the 
+  % relationship between multiplication and addition.
 
-  Unfortunately, semiclassical multiplication requires direct measurement of $R_x$
-  or $R_y$, which would collapse the superposition, so a different approach was
-  needed.
+  % Unfortunately, semiclassical multiplication requires direct measurement of $R_x$
+  % or $R_y$, which would collapse the superposition, so a different approach was
+  % needed.
 
@@
   operation, typically used to transform a qubit register from the
-  computational basis (binary) to the fourier basis (phase).  The QFT operation 
-  is defined in great detail by Perez et al.~\cite{quantum_arithmetic}.
+  computational basis (binary) to the fourier basis (phase).~\cite{quantum_arithmetic}.
 
-  To summarize, given a qubit register $R_x=|x\rangle$
-  with $n$ qubits in the computational basis, there are $d=2^n$ potential states $|k\rangle$
-  in $|x\rangle$ = $\{|0\rangle, |1\rangle, \ldots, |d-1\rangle\}$, the QFT operation in this
-  basis would be defined as:
+  % To summarize, given a qubit register $R_x=|x\rangle$
+  % with $n$ qubits in the computational basis, there are $d=2^n$ potential states $|k\rangle$
+  % in $|x\rangle$ = $\{|0\rangle, |1\rangle, \ldots, |d-1\rangle\}$, the QFT operation in this
+  % basis would be defined as:
 
-  \begin{equation}\label{eqn:QFT}
-    QFT|x\rangle = \frac{1}{\sqrt{d}} \sum_{k=0}^{d-1}e^{i{\frac{2\pi x k}{d}}}|k\rangle
-  \end{equation}
+  % \begin{equation}\label{eqn:QFT}
+  %   QFT|x\rangle = \frac{1}{\sqrt{d}} \sum_{k=0}^{d-1}e^{i{\frac{2\pi x k}{d}}}|k\rangle
+  % \end{equation}
 
-  *It is worth noting that in some cases, a QFT on some $R_x$ may require a series of SWAP
-  operations $\{ SWP(q_0,q_{n-1}), SWP(q_1,q_{n-2}), \ldots, SWP(q_{\frac{n}{2}-1},q_{\frac{n}{2}})\}$
-  in order for future arithmetic to work as expected.
+  % *It is worth noting that in some cases, a QFT on some $R_x$ may require a series of SWAP
+  % operations $\{ SWP(q_0,q_{n-1}), SWP(q_1,q_{n-2}), \ldots, SWP(q_{\frac{n}{2}-1},q_{\frac{n}{2}})\}$
+  % in order for future arithmetic to work as expected.
 
-  Once in the fourier basis, a specific number $x$ may be encoded by applying some
-  rotation $\omega_k$ to qubits $q_k \in R_x | q_k=R_x[k]$. The rotation $\omega_k$ applied
-  to each qubit $q_k$ can be defined as $\omega_k = \omega^{x k} = e^{i \frac{2\pi x k}{d}}$.
+  % Once in the fourier basis, a specific number $x$ may be encoded by applying some
+  % rotation $\omega_k$ to qubits $q_k \in R_x | q_k=R_x[k]$. The rotation $\omega_k$ applied
+  % to each qubit $q_k$ can be defined as $\omega_k = \omega^{x k} = e^{i \frac{2\pi x k}{d}}$~\cite{quantum_arithmetic}.
 
@@
 
-  Addition of two qubit registers $R_a$ in state $|a\rangle$ and $R_b$ in state 
-  $\phi(b)\rangle$ in the fourier basis 
-  ($\phi ADD(|a\rangle, |b\rangle)=|a + b\rangle$) may be performed by applying
-  controlled rotation gates $R_k$ which rotate qubits $b_j \in R_b$ by 
-  $\omega_j=e^\frac{2\pi i}{2^j}$ about the $z$-axis for each 
-  qubit $a_l | l \ge k, j=1+l-k$~\cite{quantum_arithmetic}.
+  To summarize, the QFT domain allows addition to be done through rotations in another basis,
+  and these rotations can be scaled by some constant $c$, which in practice also scales the 
+  operand by $c$. Multiplication between values encoded in registers $R_x$ and $R_y$ can then be performed
+  out-of-place into $R_z$ by conditionally adding the full value encoded in $R_x$ to $R_z$ for each qubit 
+  $q_i$ in $R_y$, such that each of these register-wide additions are performed as controlled operations 
+  which will only occur if $q_i=|1\rangle$, and that these additions are also scaled by $c=2^i$.
 
-  Multiplication in the quantum fourier domain can be done similarly. In terms of
-  a quantum circuit generation implementation, simply treat the previously defined
-  addition method as a function which adds the value of one register to another,
-  and add some constant multiple $C$ as a parameter, adjusting $\omega_j$ to 
-  $\omega_{j,C}=e^{C\cdot \frac{2\pi i}{2^j}}$. Now, to send the product of the two values in $R_x$
-  and $R_y$ to $R_z$, do as follows: Add $|R_y|$ controlled $\phi ADD(R, q_c, C)$ gates to each
-  $q_x$ in $R_x$, which will add the value of $|C\cdot x\rangle$ to $R_z$ where $C=2^u$ for
-  each $q_u \in R_y \iff q_y = |1\rangle$. This is, in essence, performing repeated scaled addition from $R_x$ onto
-  $R_z$, but the scaling factor is the powers of two corresponding to qubits in $R_y$, which
-  in tandem is cumulatively equivalent to adding $|x\cdot y\rangle$ to $R_z$~\cite{quantum_arithmetic}.
+  The details of operations such as addition and multiplication are described at great
+  lengths in the cited works, and interested readers are recommended to seek assistance
+  there for further explanation~\cite{quantum_arithmetic}.
+
+  % Addition of two qubit registers $R_a$ in state $|a\rangle$ and $R_b$ in state 
+  % $\phi(b)\rangle$ in the fourier basis 
+  % ($\phi ADD(|a\rangle, |b\rangle)=|a + b\rangle$) may be performed by applying
+  % controlled rotation gates $R_k$ which rotate qubits $b_j \in R_b$ by 
+  % $\omega_j=e^\frac{2\pi i}{2^j}$ about the $z$-axis for each 
+  % qubit $a_l | l \ge k, j=1+l-k$~\cite{quantum_arithmetic}.
+
+  % Multiplication in the quantum fourier domain can be done similarly. In terms of
+  % a quantum circuit generation implementation, simply treat the previously defined
+  % addition method as a function which adds the value of one register to another,
+  % and add some constant multiple $C$ as a parameter, adjusting $\omega_j$ to 
+  % $\omega_{j,C}=e^{C\cdot \frac{2\pi i}{2^j}}$. Now, to send the product of the two values in $R_x$
+  % and $R_y$ to $R_z$, do as follows: Add $|R_y|$ controlled $\phi ADD(R, q_c, C)$ gates to each
+  % $q_x$ in $R_x$, which will add the value of $|C\cdot x\rangle$ to $R_z$ where $C=2^u$ for
+  % each $q_u \in R_y$ as a controlled operation requiring that $q_u = |1\rangle$. 
+  % This is, in essence, performing repeated scaled addition from $R_x$ onto
+  % $R_z$, but the scaling factor is the powers of two corresponding to qubits in $R_y$, which
+  % in tandem is cumulatively equivalent to adding $|x\cdot y\rangle$ to $R_z$~\cite{quantum_arithmetic}.
 
@@
   the $\phi MULT(R_x, R_y)$ operation described at the end of section 
-  \ \ref{sec:qft_arithmetic}.
+  \ \ref{sec:qft_arithmetic}. Quantum computing operations can be represented as unitary
+  matrices, so for any $MULT(R_x, R_y)$, the adjoint operation $MULT^\dagger(R_x,R_y)$ will 
+  return all effected registers to their original states. The only change remaining after
+  applying the multiplication adjoint is that which was done by the oracle; the entangled state
+  of the target qubit has a flipped phase only in those states which resulted in our desired
+  semiprime was computed as an output- the states in which our prime factors reside.
 
@@
   The temporary solution we found was to simply decrease the size of $R_x$ and $R_y$ to 
-  $\lceil \log_2(\frac{N}{3})\rceil$, and set the size of $R_z$ to double that, to ensure no
-  further overflow could occur.
+  $n_x=\lceil \log_2(\frac{N}{3})\rceil$, and set the size of $R_z$ to double that, to ensure no
+  further overflow could occur. The size of $R_x$ and $R_y$ comes from the fact that $2$ and $3$ may
+  be considered trivial factors, so no number $p \le N/3$ will result as a factor. 
+  $\lceil\log_2(\frac{N}{3})\rceil$ is a simple computation to find the minimum number of bits required
+  to represent any number $\le \frac{N}{3}$ in binary, as would be encoded in the qubit registers. The
+  size of $R_z$ being double the size of $R_x$ or $R_y$ is based on the fact that the largest resultant
+  multiple from any value in $R_x$ or $R_y$ can be approximated as ${(2^{n_x})}^2=2^{2\cdot n_x}$, which 
+  in turn would require $2\cdot n_x$ bits to be safely represented.
 
@@
 
+Our implementation of Quantum Semiprime Factoring with Grover's Algorithm is a fully
+generalized circuit-building algorithm which can take any semiprime $N$ and return
+unique prime factors $p$ and $q$ with accuracy asymptotically approaching $100\%$~\cite{quantumfactoring_github}. 
+The program automatically calculates the required number of qubits for each register,
+and initializes a custom instance of Grover's oracle to check for the provided value $N$.
+The simulation uses statevectors to track the superposition of the circuit and apply
+gates as their corresponding matrices. The circuits are run numerous times, then
+correctness is checked across those runs to find the statistic for $\%$ acc, as seen 
+in Figure~\ref{fig:FIGURC1}.
+
+\begin{figure}[ht]\label{fig:FIGURC1}
+\centering
+\includegraphics[width=7.9cm]{results.png}
+% \includegraphics[width=15.8cm]{grover_inversion.png}
+% \includegraphics[width=14cm]{grover_inversion.png}
+\caption{Example program output for $N=143$. The state of each qubit 
+when measured is either $|1\rangle$ or $|0\rangle$, and registers are separated by underscores, as seen
+after `Full result: $\dots$'}
+\end{figure}
+
 To date, we have preliminary results based on CUDA-Q simulation of quantum circuits, 
@@
 and search them for modulo zero factoring.
-
-This work is still in progress, but we have a working implementation of Grover's 
-algorithm with the CUDA-Q simulation which can estimate the time to factor any 
-semiprime up to the current scaling limits of the CUDA-Q simulation\cite{quantumfactoring_github}.
 
@@
 
-  Due to the exploratory nature of this work, the initially sub-optimal nature of our 
-  implementation is intentional, because it allows for a more direct view of the inputs
-  and outputs in our circuit.
-
   For context, our current implementation uses $4 \lceil \log_2(\frac{N}{3})\rceil$ qubits
@@
   prime factors of up to $35$-bit semiprimes, using up to a total of $65$ qubits. 
-  The limiting factor for our simulations is VRAM, so it is expected that after implementing 
+  The limiting factor for problem scaling in our simulations is memory, so it is expected that after implementing 
   the optimizations from S. Whitlock et al.,\ our simulations should be able to scale up to 
   $18$-bit semiprimes on the current equipment.
+
+  To be blatantly clear, this Grover's-based implementation is more of a proof-of-concept than
+  a truly preferrable design over Shor's. The longer time complexity of this implementation
+  is expected to coincide with increased error if it were to be run on an actual quantum computer,
+  and the implementation in it's current state has greater time complexity than current classical
+  methods like GNSF~\cite{Bai2016,quantum_factoring}.
 
@@
 
-Grover's algorithm has been demonstrated to be a highly versatile function,
-able to invert almost any function that can be implemented on a quantum 
-computer with inputs in superposition.
+Grover's algorithm is highly versatile, and has been implemented in a
+generalized fashion, such that it is effectively plug-and-play, with the
+only necessary parameter being the value to search for. Everything else is
+determined by the function that is chosen for $F(x, \dots)$.
 
-Quantum methods of SP factoring have been developing at a quick pace,
-and it will most likely not be very long before practical examples
-of quantum advantage may be seen.
+Despite the large time complexity, even this sub-optimal implementation requires
+fewer qubits than Shor's algorithm, and constructing the program in such a 
+generalized manner has made it trivial to use Grover's algorithm for nearly any other
+such function that can take as input registers that are in uniform superposition.
 
@@
 search term $M$, which should reduce the number of qubits needed from 
-$4 \lceil \log_2(\frac{N}{3})\rceil$ to $2n-5$.
+$4 \lceil \log_2(\frac{N}{3})\rceil$ to $2n-5$\ \cite{quantum_factoring}.
 
